---
title: "Model to predict miles per gallon using weigth,transmission mode and 1/4 mile time"
author: "Shubhanshu Mohan Srivastava"
date: "1 September 2018"
output: ioslides_presentation
---

## Project objective

The aim of the project is to predict the miles per gallon using weight,transmission mode and 1/4 mile time.Linear model will be used for the prediction.As a part of the project a web application will be developed to predict the miles per gallon by providing the required details.

Requisites of the project:<br>
1. mtcars dataset(available in R)<br>
2. shiny(web framework by Rstudio)<br>


## Data

The dataset being used to train the model is mtcars dataset.

```{r,echo=FALSE,comment=" "}
data(mtcars)
head(mtcars)
```

We can see that that the mtcars dataset is a good choice to develop a prediction model for the miles per gallon.

## Plots

The following decision tree will be used for prediction:

```{r,echo=FALSE,cache=TRUE}
par(mfrow=c(1,3))
    plot(mtcars$mpg~mtcars$wt,xlab="weight",ylab="miles per gallon")
    plot(mtcars$mpg~mtcars$qsec,xlab="1/4 mile time",ylab ="miles per gallon")
    plot(mtcars$mpg~mtcars$am,xlab="transmission mode",ylab="miles per gallon")
```

## Functionality of the application

The application will provide an interface to enter the weight,transmission mode and 1/4 mile time.These details will be used to predict the mpg of the car.

The following details will be needed:

1.Weight<br>
2.Transmission mode<br>
3.1/4 mile time<br>


## Link to the project

The web application can be found [Here](https://shubhanshu.shinyapps.io/mtcars_app/)

The code for the application can be found [Here](https://github.com/shubhanshumohan/mtcars_app)






